---
format: docx
---

## Behavioral Health Services
```{r}
bhs_keywords <- c(
  "mental disorder", " psychiatric",
  " therapy", " emotional health", " stabilization", "crisis hotline",
  " respite", "depression", " anxiety", 
  " behavioral health",
  " mental health", " anger management",
  " behavioral disorders",
  "psychiatric conditions",
  "counseling and therapy",
  " mental illness", " psychologist", "neurodivergen"
)
```

## Substance Use Treatment
```{r}
sut_keywords <- c(
  " substance", "addiction", "drugs", "alcohol", "sobriety", "dependence",
  "rehabilitation", "detox", "narcotics", "overdose", "rehab", "drug addiction",
  "substance use", "addict",
  "substance abuse", "drinking",
  "harm reduction",
  "inpatient rehabilitation centers",
  "needle exchange",
  "supervised consumption",
  "alcoholics anonymous", "marijuana", "cocaine", "heroin", "methamphetamine", 
  "mdma", "cannabis", "nicotine", "opiod", "sober"
)
```

## Housing Assistance
```{r}
ha_keywords <- c(
  " housing", "shelters","homeless", "boarding", " homes", " rehousing",
  "unhoused", "accommodation",
  "housing assistance",
  "stable housing",
  "housing solutions",
  "emergency shelters",
  "supportive housing options",
  "housing instability",
  "transitional housing",
  "temporary housing",
  "permanent housing",
  "boarding homes",
  "long-term housing",
  "daily living",
  "emergency homeless shelters",
  "short-term accommodations",
  "affordable housing",
  "low-income residents"
)
```

## Healthcare Services
```{r}
hcs_keywords <- c(
  "healthcare", "medical", "medicine",
  "clinic", "hospital", "medication", "physician", "doctor",
  "injuries", "surgeries", "prescription",
  "healthcare services",
  "primary care",
  "hospital",
  "health education",
  "medical treatment",
  "primary healthcare",
  "medical facilities", "nurse",
  "preventive care",
  "disease prevention",
  "healthy lifestyle", "physical therapy", "occupational therapy",
  "speech therapy"
)
```

## Community Policing Initiatives
```{r}
cpi_keywords <- c(
  "community policing",
  "law enforcement",
  "public safety",
  "police officers",
  "community policing training",
  "law enforcement",
  "educate officers",
  " patrol", 
  "neighborhood watch",
  "crime prevention",
  "police-community relations",
  "law enforcement outreach",
  "police partnership",
  "community safety programs",
  "crime reporting",
  "police visibility",
  "local policing"
)
```

## Legal Aid Advocacy
```{r}
laa_keywords <- c(
  "legal", "representation",
  "attorney", "defender", "represent", "case", "law", "lawyer", "rights",
  "legal aid and advocacy",
  "legal support",
  "legal advice",
  "justice reform",
  "legal advocacy",
  "legal advocate",
  "justice",
  "legal issues",
  "public defender",
  "criminal case",
  "legal aid organizations",
  "legal assistance",
  "policy advocacy",
  "legal reform",
  "criminal defense",
  "legal help"
)
```

## Legal Diversion Supports
```{r}
lds_keywords <- c(
  "legal diversion supports",
  "pretrial",
  "diversion",
  "criminal diversion",
  "legal diversion",
  "pretrial diversion",
  "pretrial supervision",
  "risk assessment",
  "specialty court",
  "reduce incarceration",
  "pretrial supervision",
  "oversight and support",
  "awaiting trial",
  "monitoring and compliance",
  "evaluating risk",
  "drug court",
  "mental health court",
  "special court", "court"
)

```

## Re-entry Support
```{r}
# add incarceration keywords to this

res_keywords <- c(
  "reentry", "transitioning", "family support",
  "job", " loan", "financial need", "utility bill",
  "reentry support",
  "employment",
  "housing", "utilities",
  "education",
  "social integration",
  "reintegrate",
  "re-entry",
  "vocation",
  "job training",
  "training",
  "workforce",
  "vocational rehabilitation",
  "disabilities",
  "accommodations",
  "stable housing",
  "skill development",
  "adult education",
  "literacy",
  "GED",
  "family support",
  "social support",
  "family counseling",
  "supportive social networks",
  "community groups",
  "social support",
  "childcare", "baby",
  "transportation",
  "public transport",
  "public transit",
  "bus",
  "trains",
  "essential services", "secondhand", "thrift store",
  "computer", "writing", "reading", "printer", "tax", "internet",
  "adult education"
)
```

## Community Engagement and Awareness
```{r}
cea_keywords <- c(
  "community engagement", "awareness", "forums", "participation", 
  "partnerships", "community contribution", "public participation",
  "community engagement and awareness", "stakeholder engagement",
  "local issues", "community leader", "local partnership",
  "outreach programs", "community participation",
  "public meetings", "grassroots",
  "raise awareness", "awareness campaign"
)
```

## Incarcerated
```{r}
inc_keywords <- c("incarcerated", 
                              "imprisoned",
                              "misdemeanor",
                              "jail",
                              "detained",
                              "behind bars",
                              "incarceration",
                              "convict",
                              "remanded",
                              "put away",
                              "interned",
                              "prison",
                              "penitentiary",
                              "correctional",
                              "reform",
                              "justice system",
                              "sentence",
                              "criminal",
                              "offender",
                              "felon",
                  "court-mandated"
                            )
```

## Food Assistance
```{r}
fa_keywords <- c(
    "food assistance",
    "food aid",
    "nutritional support",
    "food program", "fruits",
    "food distribution",
    "food bank",
    "meal program",
    "emergency food services",
    "food voucher", "vegetables",
    "food stamps",
    "community kitchen",
    "pantry services",
    "grocery assistance",
    "meal delivery",
    "food relief",
    "food security",
    "hunger relief",
    "food recovery",
    "nutrition programs", "kitchen",
    "food subsidies", 
    "food", "nutrition", "meal", "pantry", "grocery", "hunger"
)
```

## Military
```{r}
mil_keywords <- c("army", "veteran", "military", "navy", "air force")
```

## Women and Motherhood
```{r}
wm_keywords <- c("maternal", "women", "childbirth", "birth", "prenatal",
                 "diaper", "infant", "nursing", "maternal health", "maternity",
                 "women's health", "postpartum")
```

## Children and Youth
```{r}
child_keywords <- c(
  "children", "youth", "kid", "adolescent", "early learning",
  "junior", "teen", "kindergarten", "school disctict", 
  "afterschool", "school", "boy", "girl", "child"
)
```

## Chronic Disease/ Disorder
```{r}
dis_keywords <- c("heart disease", "diabetes", "liver", "cancer", 
                "sexually transmitted disease", "sexually transmitted infection", 
                "std", "alzheimer", "chronic disease", "hiv", "cleft", "affected",
                "screening", "support")
```

## Animals
```{r}
ani_keywords <- c(
  "animal protection", "veterinarian", "pets", 
  "wildlife protection", "humane", "domesticated", " pet ", "neuter", "spay",
  "animal health"
)
```


## Immigrants
```{r}
imm_keywords <- c("immigration", "refugee", "asylum", "immigrant")
```

## Elderly
```{r}
eld_keywords <-  c("elder", "senior citizen", "older adult", "senior", "aged",
                   "geriatric", "retire")
```

## Disability
```{r}
dabi_keywords <-  c(
  "disability", "autism", "asperger", "disabled", " ada ", 
  "special needs", "impaired", "impairment", "blind", "deaf", "wheelchair",
  "accessibility", "differently-abled"
)
```

## Disaster Relief
```{r}
dr_keywords <- c(
  "natural disaster", "earthquake", "hurricane", 
  "tornado", "flood", "wildfire", "tsunami", "volcano", 
  "landslide", "drought", "severe weather", "evacuation", 
  "disaster relief", "crisis management",
  "rescue operations", "disaster recovery", "preparedness",
  "disaster"
)
```

## Negating phrases
```{r}
neg_keywords <- c(
  " no", "not assist with", "not serve", "not help", "not provide", "not offer",
  "not supply", "not help with"
)
```

## Basic Needs
```{r}
bn_keywords <- c(
  "food", "clothing", "clothes", "shoes", "meal", "grocery", "groceries", 
  "shower", "hygiene", "garment" 
)
```

# Save data
```{r}
path <- here::here("data", "keyword_lists.RData")
save(bhs_keywords, sut_keywords, ha_keywords, hcs_keywords, cpi_keywords, 
     laa_keywords, lds_keywords, res_keywords, cea_keywords,
     fa_keywords, inc_keywords, mil_keywords, wm_keywords, child_keywords,
     dis_keywords, ani_keywords, imm_keywords, eld_keywords, dabi_keywords,
     neg_keywords, bn_keywords,
     file = path)
```

```{r}
rm(list = ls())
```
