---
format: docx
---

## Outpatient
```{r}
outpatient_keywords <- c("outpatient", "non-residential", "external patient", "day patient",
                         "counseling", "group therapy", "clinic", "consultation",
                         "psychiatric evaluation", "appointment", "consultation", "virtual",
                         "client's home", "telehealth", "referral", "support group", "screen",
                         "helpline", "text", "day center", "hour")
```

## Inpatient Facilities
```{r}
inpatient_keywords <- c("inpatient", "extended hospitalization",
                        "hospitaliz", "overnight", "admitted", "surger", 
                        "residential")
```

## Residential Facilities
```{r}
res_keywords <- c("treatment homes", "residential")
```

## Crisis Intervention

```{r}
crisis_keywords <- c("crisis")
```

## Emergency

```{r}
emergency_keywords <- c("emergency")
```

## Harm Reduction Services
```{r}
harm_reduction_keywords <- c("harm reduction", "needle exchange", 
                             "supervised consumption", "naloxone", "safer use")
```

## Support Groups
```{r}
support_group_keywords <-  c("support group", "anonymous", "peer", "group")
```

## Transitional Housing Programs
```{r}
trans_hous_keywords <- c("transitional housing", "temporary housing", 
                         "temporary shelter", "supportive housing", 
                         "transitional shelter")
```

## Boarding Homes
```{r}
boarding_homes <- c("boarding home" )
```

## Emergency Homeless Shelters
```{r}
emergency_homeless_keywords <- c("emergency housing", "emergency accommodation",
                                 "crisis shelter", "rescue shelter", 
                                 "urgent shelter", "urgent housing", "homeless")
```

## Rapid Rehousing 
```{r}
rapid_rehousing_keywords <- c("rapid rehousing", "homeless")
```

## Supportive Housing Programs
```{r}
supportive_housing_keywords <- c("supportive housing", 
                                 "service-enriched housing", 
                                 "supportive living")
```

## County-Funded “Affordable Housing” Programs
```{r}
county_funded_housing_keywords <- c("government", "subsidized", "county-funded",
                                    "affordable housing", "publicly funded",
                                    "county funded")
```

## Primary Healthcare Clinic
```{r}
primary_hcs_keywords <- c("routine", "check-ups", "preventive care", "common illness",
                 "common injuries", "primary care", "general", "preventive")
```

## Health Education Programs
```{r}
health_edu_keywords <- c("health education", "health awareness", 
                         "welness education", "health training", 
                         "health literacy", "health coaching", 
                         "nutritional education")
```

## Access to Medication and Medical Treatment
```{r}
medical_access_keywords <-  c("prescription assistance", "drug access",
                              "affordable health", "volunteer clinic",
                              "patient support services", "low cost clinic",
                              "community health clinic", "free clinic")
```

## Programs that Build Positive Relationships Between Law Enforcement and the Community
```{r}
law_community_keywords <- c("community policing", "community partnership",
                            "trust-building", "community outreach", 
                            "neighborhood watch", "neighborhood outreach",
                            "transparency initiatives", ""
                            )
```

## Community Policing Training for Law Enforcement Officers
```{r}
police_training <- c("active listening", "diversity training", 
                     "conflict resolution", "ethical policing", "de-escalation",
                     "cultural competency")
```

## Public Defenders
```{r}
pub_def_keywords <- c("public defender", "defensive counsel", 
                      "legal aid atorney", "defense lawyer", 
                      "state-funded attorney", "defence", "defend")
```

## Legal Aid Organizations
```{r}
la_orgs_keywords <- c("legal aid organization", "public interest law firm",
                      "law clinic", "nonprofit legal service",
                      "legal center")
```

## Advocacy Groups Working on Criminal Justice Reform
```{r}
advocacy_group_keywords <- c("advocacy group", "justice reform group",
                             "civil rights group", "advocate", "reform")
```

## Pretrial Diversion Programs
```{r}
pretrial_div_keywords <- c("pretrial diversion", "pretrial release", 
                       "pretrial intervention", "judicial diversion", 
                       "alternative sentencing", "diversion")
```

## Pretrial Supervision Services
```{r}
pretrial_sup_keywords <- c("pretrial monitoring", "supervised release",
                           "pretrial probation", "pretrial assessment", 
                           "conditional release", "bail supervision", 
                           "judicial supervision")
```

## Risk Assessment Programs
```{r}
risk_assessment_keywords <- c("risk assessment", "risk evaluation", 
                              "pretrial risk", "recidivism risk", "risk",
                              "pretrial screening")
```

## Specialty Courts
```{r}
specialty_courts_keywords <- c("specialty court", "diversion court", 
                               "treatment court", "special court", "court")
```

## Reentry Programs and Support Services
```{r}
reentry_program_keywords <- c("reentry", "reintegration")
```

## Employment and Vocational Programs
```{r}
employ_keywords <- c("job", "job training programs",
  "vocational training services", "career development programs",
  "workforce development initiatives", "employment skills training",
  "occupational training programs", "skill enhancement programs",
  "job readiness programs", "career counseling services",
  "apprenticeship programs", "hands-on training",
  "technical skills development", "employment placement services",
  "industry certifications", "job search assistance",
  "resume writing workshops", "interview preparation",
  "career pathways", "soft skills training",
  "labor market information", "supportive employment",
  "community job fairs", "on-the-job training",
  "skills assessment", "work experience programs", "training", "career")
```

## Housing Assistance for Individuals Reentering Society
```{r}
hous_rees_keywords <- c("transitional housing", "housing", "accommodation",
  "reentry housing", "supportive housing services",
  "affordable housing", "permanent supportive housing",
  "temporary housing", "reintegration housing", "stable housing initiatives",
  "housing navigation services", "subsidized housing for reentrants",
  "homeless prevention programs", "case management for housing",
  "rapid rehousing programs", "long-term housing", 
  "family reunification housing", "safe housing", "housing counseling",
  "employment and housing support", "housing stability programs")
```

## Education and Skill Development
```{r}
edu_keywords <-  c("retrain", "career transition", "adult learning",
  "education", "skill refresh", "personal development", "continuing education",
  "train", "skill development")
```

## Family and Social Support
```{r}
family_support_keywords <- c("family reintegration", "social reintegration",
  "community support", "peer support", "family counseling", "mentorship",
  "family", "social", "relationship"
)
```

## Transportation Services
```{r}
transport_keywords <- c("transport", "transit", "bus", "commute", " ride")
```

## Community Forums and Education Sessions
```{r}
commu_forum_edu_keywords <- c("public meeting", "educational event", 
                              "community forum", "community meeting",
                              "education session", "forum"
                              )
```

## Outreach Programs to Raise Awareness About Available Resources
```{r}
outreach_keywords <- c("outreach", "available resources", "resource education",
                       "resource accessibility", "resource connection event",
                       "resource fair")
```

## Collaboration with Community Leaders and Organizations
```{r}
collab_keywords <- c("partnership", "community alliance", "coalition",
                     "collaborative effort", "community cooperation")
```

# Save data
```{r}
path <- here::here("data", "sub_cat_keyword_lists.RData")

save(outpatient_keywords, inpatient_keywords, res_keywords, crisis_keywords,
     emergency_keywords, harm_reduction_keywords, support_group_keywords,
     trans_hous_keywords, boarding_homes, emergency_homeless_keywords,
     rapid_rehousing_keywords, supportive_housing_keywords, 
     county_funded_housing_keywords, primary_hcs_keywords, health_edu_keywords,
     medical_access_keywords, law_community_keywords, police_training,
     pub_def_keywords, la_orgs_keywords, advocacy_group_keywords, 
     pretrial_div_keywords, pretrial_sup_keywords, risk_assessment_keywords,
     specialty_courts_keywords, reentry_program_keywords, employ_keywords,
     hous_rees_keywords, edu_keywords, family_support_keywords, 
     transport_keywords, commu_forum_edu_keywords, outreach_keywords, 
     collab_keywords,
     file = path)
```

```{r}
rm(list = ls())
```